Improvement of Korean Morphological Analysis System \\Through Transformer-Based Re-Ranking

### 2023-12-04 contents/draft.tex
Respond the reviewer's comment: - Table 5: Sejong data shows poor performance in other approaches and proposed with rerank shows the better performance (from Table 3 and 4). However, Table 5 does not show any huge improvement compared to other approaches. Did you try with other dataset? Not sure how much improvement it will show with others.

    The proposed transformer-based re-ranking technique consistently improved the results of existing morphological analysis models, showcasing its potential to enhance outcomes in the field of Korean morphological analysis (refer to Table~\ref{tab:differences-with-previous-studies}).
    These findings suggest that it opens up new possibilities by further refining the results of traditional machine-learning models.
    In a comparative analysis with previous studies, particularly those predominantly focused on the Sejong corpus, we observed performance improvements.
    While direct comparisons are challenging due to slight differences in implementation conditions and evaluation criteria, the proposed dictionary-based morphological analysis model, when coupled with a re-ranking model, achieved a performance comparable to existing research, though not at the latest research results.

    It's worth noting that the entire morphological analysis model, inclusive of the two-stage re-ranking model, may not meet the requirements for real-time processing due to various inherent factors.
    The complex re-ranking process evaluates all secondary paths generated by the morphological analysis, consuming significant computational resources and processing power.
    This demand for substantial resources, coupled with the necessity for millisecond-level response times in real-time applications, can introduce unacceptable latency.
    The system's current design may not efficiently handle the continuous data stream and high-throughput needed, potentially leading to user-perceptible delays.

    However, there is potential for performance enhancement.
    By incorporating cases where ranks are altered through the re-ranking model as feedback to the dictionary-based morphological analysis model, it becomes plausible to achieve near-improved morphological analysis performance.
    The enhanced dictionary-based morphological analysis model can then serve as input to the re-ranking model, fostering iterative improvement in the overall morphological analysis model through this feedback loop.

>>>>

    The proposed transformer-based re-ranking technique consistently improved the results of existing morphological analysis models, showcasing its potential to enhance outcomes in the field of Korean morphological analysis (refer to Table~\ref{tab:differences-with-previous-studies}).
    Our approach opens new avenues by further refining the results of traditional machine-learning models.
    Our study utilized the same dataset from the Sejong corpus as employed in prior research ~\cite{MinJW2019, MinJW2020, MinJW2022, MinJW2018, NaSH2015, NaSH2014, NaSH2018, SongHJ2019, SongHJ2020}.

    While direct comparisons can be challenging due to minor differences in implementation conditions and evaluation criteria, our dictionary-based morphological analysis model, augmented with a re-ranking model, achieved performance levels comparable to those of existing research.
    As mentioned in Section~\ref{subsec:evaluation-metrics}, that evaluation standards can vary slightly across different studies.
    Additionally, the process of transforming training data might lead to varying amounts of data being removed or excluded, which could affect the precision of direct comparisons.

    Our entire morphological analysis model, including the two-stage re-ranking model, might not yet be optimized for real-time processing due to its computational intensity.
    The re-ranking process, which evaluates all secondary paths generated by the morphological analysis, demands significant computational resources and power.
    This requirement, combined with the need for rapid response times in real-time applications, could introduce latency that may not be acceptable for certain use cases.
    The current design of our system may not efficiently manage continuous data streams and the high throughput necessary for real-time operation, potentially leading to noticeable delays for users.

    However, we recognize the potential for performance enhancement.
    By using cases where ranks are altered through the re-ranking model as feedback for the dictionary-based morphological analysis model, it becomes feasible to achieve near-improved morphological analysis performance.
    This enhanced dictionary-based model could then be re-input into the re-ranking model, creating a feedback loop that fosters iterative improvements in the overall morphological analysis process.
    This approach not only demonstrates the effectiveness of our model in a controlled environment but also indicates the potential for broader applicability and adaptability across various types of Korean text datasets.
